oolong: An R package for validating  automated content analysis tools

### 2020-07-21 paper/paper.rmd
talk about @revelunt too, ref #31
fix punct issue, ref #31

Validity is a requirement of content analysis [@krippendorff2018content; @neuendorf2016content]. Validation of automated methods has been called for by many scholars, e.g. @grimmer2013text; @ribeiro2016sentibench; @van2018communication. The paper by @dimaggio2013exploiting conceptualizes validation of automated methods as three different operations and the three operations supplement each other. These three operations are: 1) *statistical* validation -- to see if the model results agree with the assumptions of the model. Examples of statistical validation are calculation of pointwise mutual information, perplexity or semantic coherence of a topic model. 2) *semantic* validation -- to see if the model results are semantically meaningful. This procedure involves comparing model results with human judgment [@grimmer2011general]. 3) *predictive* validation -- to see if the model results can predict external events [@quinn2010analyze]. For example, one can study whether external events can explain surges in attention to a topic extracted by a topic model.

@@

Oolong focuses on semantic validation. The package provides the "human-in-the-loop" semantic validation procedures suggested by @chang2009reading and @song2020validations. The procedure proposed by @chang2009reading has been adopted in subsequent social science studies as the gold standard to validate topic models, e.g. @bohr2020reporting, @chuang2015topiccheck, and @miller2017australia.

>>>>

Validity is a requirement of content analysis [@krippendorff2018content; @neuendorf2016content]. Validation of automated methods has been called for by many scholars, e.g. @grimmer2013text; @ribeiro2016sentibench; @van2018communication. The paper by @dimaggio2013exploiting conceptualizes validation of automated methods as three different operations and the three operations supplement each other. These three operations are: 1) *statistical* validation --to see if the model results agree with the assumptions of the model. Examples of statistical validation are calculation of pointwise mutual information, perplexity or semantic coherence of a topic model; 2) *semantic* validation --to see if the model results are semantically making sense. This procedure involves comparing model results with human judgment [@grimmer2011general]; 3) *predictive* validation --to see if the model results can predict external events [@quinn2010analyze]. For example, one can study whether external events can explain surges in attention to a topic extracted by a topic model.

@@

Oolong focuses on semantic validation. The package provides the "human-in-the-loop" semantic validation procedures suggested by @chang2009reading and @song2020validations. The procedure proposed by @chang2009reading has been adopted in subsequent social science studies as the gold standard to validate topic models, e.g. @bohr2020reporting, @chuang2015topiccheck, and @miller2017australia. The procedure proposed by @song2020validations emphasizes both criterion validity and interrater reliability.
